---
title: "Analysis of Structural Tubes"
author: "Riley M. Anderson, PhD"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
graphics: yes
output:
  github_document:
    toc: yes
    toc_depth: 5
    pandoc_args: --webtex
  html_document:
    keep_md: yes
    theme: readable
    mathjax: default
  html_notebook:
    code_folding: hide
    theme: readable
    mathjax: default
  pdf_document:
    toc: yes
header-includes:
  \usepackage{float}
  \floatplacement{figure}{H}
editor_options:
  chunk_output_type: console
---

```{r setup, include = F}
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Knitr Options
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Set root directory to the project directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())


# Set default knitr options: 
# Suppress warnings and messages, cache chunks, 
#  set default figure size to 6x8 at 300 dpi, and save a png and pdf
knitr::opts_chunk$set(warning = F, message = F, collapse = T, cache = T,
    fig.height = 6, fig.width = 8, dpi = 300, # 6x8" @ 300dpi:1800x2400=4.3MP
    dev = c('png', 'pdf'), dev.args = list(pdf = list(onefile = F)))

```



## Overview

A comparison of commonly available structural tubes for use in marine applications.

The table shows:

* moment of inertia (in^4^)
* modulus of elasticity (PSI)
* deflection of a 100 lb centered point load at 6, 5, 4, 3, & 2 feet of span
* material cost ($/ft)
* material density (lbs/in^3^)
* material weight (lbs/ft)

For each of 5 tubes of various materials and sizes:

* FRP (fiberglass-reinforced polyester)
  + 1.5" x 0.125" wall thickness
  + 1.75" x 0.125" wall thickness
  + 2" x 0.25" wall thickness
* 316 Stainless steel
  + 1.5" x 0.065" wall thickness
* 6061 T6 Aluminum
  + 1.5" x 0.095" wall thickness


The figure shows the same data and is interactive. Hover over any point for more information. 

```{r Main_Code, include = F, cache = F}

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Setup - This code is run, but output is hidden
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Load Packages
library(tidyverse) # Needed for data wrangling: dplyr, tidyr, ggplot2
library(cowplot) # Needed for publication-quality ggplots
library(plotly)
library(knitr)

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Data Preparation
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Import datasets
#data <- read.csv("data/file.csv")


```


```{r Data_Wrangling, echo = F, comment = ""}

cnames <- c("1.5x0.125FRP",
            "1.75x0.125FRP",
            "2x0.25FRP",
            "1.5x0.06SS",
            "1.5x0.095ALU")


mat.prop <- data.frame(
  a = c(0.129, 39),
  b = c(0.212, 39),
  c = c(0.537, 39),
  d = c(0.071, 193),
  e = c(0.104, 68)
)

colnames(mat.prop) <- cnames

tmat.prop <- t(mat.prop)

cnames2 <- c("Ix", "E")

colnames(tmat.prop) <- cnames2

tmat.prop1 <- tmat.prop %>% 
  as_tibble() %>% 
  mutate(E = E * 145000) %>% 
  mutate(S_100lb_5ft = (100 * 72^3) / (48 * E * Ix),
         S_100lb_5ft = (100 * 60^3) / (48 * E * Ix),
         S_100lb_4ft = (100 * 48^3) / (48 * E * Ix),
         S_100lb_3ft = (100 * 36^3) / (48 * E * Ix),
         S_100lb_2ft = (100 * 24^3) / (48 * E * Ix)) %>% 
  mutate(price_ft = c(7.5, 8.2, 15.8, 16, 31.75),
         area_in = c(.54, .638, 1.374, .293, .419),
         dens_lbs_in3 = c(.064, 0.064, 0.64, .289, .0975),
         weight_ft = (area_in * 12) * dens_lbs_in3)

dnames <- as_tibble(cnames)

dnames <- dnames %>% 
  rename(material = value)

tubes <- bind_cols(dnames, tmat.prop1)

tubes.long <- tubes %>% 
  pivot_longer(cols = S_100lb_5ft:S_100lb_2ft, names_to = "S") %>% 
  mutate(span_length = case_when(S == "S_100lb_6ft" ~ 6,
                                 S == "S_100lb_5ft" ~ 5,
                                 S == "S_100lb_4ft" ~ 4,
                                 S == "S_100lb_3ft" ~ 3,
                                 S == "S_100lb_2ft" ~ 2)) %>% 
  rename(S_at_100lb_PL = S,
         Smax = value) %>% 
  mutate(material = factor(material))

kable(tubes, format = "markdown", digits = 3)


int.fig.data <- tubes.long %>% 
  mutate(Smax = round(Smax, 3),
         weight_ft = round(weight_ft, 2)) %>% 
  mutate(text = paste(
    "\nWeight/ft: ", weight_ft,
    "lbs\nPrice/ft: $", price_ft
  ))

```


```{r Smax_tube_IFIG, echo = F}

p <- ggplot(int.fig.data, aes(x = span_length,
                       y = Smax,
                       fill = material,
                       text = text)) +
  geom_point(size = 4,
             shape = 21,
             color = 'black') +
  geom_line(color = "gray") +
  theme_classic() +
  labs(x = "Span Length (ft) @ 100 lbf point load",
       y = "Smax \n Max Deflection (in)")


IP <- ggplotly(p, 
         layerData = 2,
         originalData = F,
         tooltip = "text")

IP

```


```{r ggplot_fig, echo = F}

p

```

## Session Information

```{r Session_Info, echo = F, comment = ""}

# Add session information to help with reproduceability
sessionInfo()


```


